---
title: "aula3"
author: "miaofang"
date: "2022/8/31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```


# 1). Data

For this exercise, you will need to load some data on lethal police violence in the United States:

```{r}
link <- "https://raw.githubusercontent.com/FLS-6497/datasets/main/aula3/PKAP_raw_data.csv"
dados <- readr::read_csv(link)
```



```{r}

#cleaning data

dados2 <- dados %>% select(race, contains("officer_")) %>% 
  mutate(race = ifelse(race == "Black", 1, 0)) %>% 
  mutate(officer_present = ifelse(officer_present == "Unknown", 1, 0)) %>% 
  mutate(officer_race = case_when(officer_race == "White" ~ 1,
                                  officer_race == "White,Unknown" ~ 1,
                                  officer_race == "White, Unknown" ~ 1,
                                  TRUE ~ 0)) %>% 
  mutate(across(c(officer_name, officer_years, officer_undercover, officer_offduty, officer_personal), ~ ifelse(.x == "Yes", 1, 0))) %>%
  mutate(officer_gender = ifelse(str_detect(officer_gender, "Female"), 1, 0)) %>% 
  select(-officer_fire) %>% 
  na.omit()
  

```


# a) Exploration of features
```{r}
dados2 %>%
  pivot_longer(-race) %>% 
  mutate(race = ifelse(race == 1, "Black", "White")) %>% 
  group_by(name, race) %>% 
  summarise(n = sum(value, na.rm = TRUE)) %>% 
  ggplot(aes(x = race, y = n)) +
  geom_col() +
  facet_wrap(~ name, scale = "free")

dados %>% distinct(officer_name)
```


# 2) Logistic classifier
```{r}

library(mlr3learners)
library(mlr3)
 dados2
 
# Training models
tsk <- as_task_classif(race ~ ., data = dados2) #. represent all the variables in the dataframe

learner <- lrn("classif.log_reg")
learner$train(tsk)

# Evaluate prediction
pred <- learner$predict(tsk)
pred$confusion  
measure <- msr("classif.acc")
pred$score(measure)
```


# 3) Training and testing

## a) Create function

Create a function to draw from the base a training sample and a test sample. For this, the function can return a list with the two samples. Also create an argument in the function that allows you to select the percentage of observations in the training sample (default will need to be 0.7).


```{r}

learner$train(tsk, row_ids = 1:120)
```

```{r}
training_model <- function(treino = 0.7){
  task <- as_task_classif(race ~ ., data = dados2) 
  split <- partition(task, ratio = treino)
  learner <-lrn("classif.log_reg")
  learner$train(task, split$train)
  pred <- learner$predict(task,split$test)
  #pred$confusion
  measure <- msr("classif.acc")
  pred$score(measure)
}

```



```{r}

experiment <- 1:500 %>% 
  map_dbl(~ training_model())

as.data.frame(experiment) %>%
  ggplot() + geom_histogram(aes(experiment), colour = "black", fill = "orange")
```

